### 2017-12-10 paper/jfp-submission/introduction.tex
mention the extension

>>>>

\paragraph{New Material}
This paper is an extension of our ICFP '16 paper of the same
name~\cite{Seidel2016-ul}.
%
In this extension we have focused on expanding our experimental evaluation.
%
First, in \S~\ref{sec:how-safe} we investigate the student programs for
which we were unable to synthesize a witness. We group the failures into
five categories, give representative examples, and suggest ways to
improve our feedback in these cases. Interestingly, we find that in the
majority of these failed cases, the programs do not actually admit a
witness in our semantics.
%
Second, in \S~\ref{sec:locating} we attempt to use our witnesses to
localize type errors with a simple heuristic. We treat the stuck term as
a sink for typing constraints, and the values it contains as sources of
constraints. We can then predict that either the stuck term or one of
the terms that \emph{produced} a value it contains is likely at fault
for the error. We compare our localizations to \ocaml and two
state-of-the-art type error localization tools, and find that we are
competitive with the state of the art.
%
Finally, we have also extended \S~\ref{sec:user-study} with an analysis
of the statistical significance of our user study results.
